\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-10 paper/paper.Rnw
Fixed Pins

\begin{document}

@@

\newpage
\spacingset{1.45} % DON'T change the spacing!
\newpage
<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
# Convert reshape2 to tidyr, melt to gather - done
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(splitstackshape)
library(readr)
library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv")
full <- read.csv("full.csv", row.names=1) 
Turk <- read.csv("turk.csv")

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
pin <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
pin <- cSplit(pin, "response_0", direction="long")
counts <- data.frame(table(pin$pic_id, pin$response_0))
counts$Var1 <- as.integer(counts$Var1)
counts$Var2 <- as.integer(counts$Var2)
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot.x, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
#colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(test_param=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
ggplot(data=subset(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")

@@

<<powerfit, dependson='setup', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + test_param + test_param*smoothed 
                  + test_param*r + test_param*n + test_param*rsgn*r + test_param*correct + (1|subj_id), data=full.sub)
@
%get table code

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\newpage
\spacingset{1.45} % DON'T change the spacing!
\newpage
<<setup, echo=FALSE, results=hide, message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
# Convert reshape2 to tidyr, melt to gather - done
#library(reshape2)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
#library(splitstackshape) - changed cSplit to unnest
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv")
full <- read.csv("full.csv", row.names=1) 
Turk <- read.csv("turk.csv")

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
pin <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
pin$response_0 <- as.integer(pin$response_0)
counts <- data.frame(table(pin$pic_id, pin$response_0))
counts$Var1 <- as.integer(counts$Var1)
counts$Var2 <- as.integer(counts$Var2)
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
#colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(test_param=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
ggplot(data=subset(pin, smoothed=="no" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="no" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")

@@

<<powerfit, dependson='setup', echo=FALSE, results=hide, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

<<timefit, dependson='powerfit', echo=FALSE, results=hide, message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + test_param + test_param*smoothed 
                  + test_param*r + test_param*n + test_param*rsgn*r + test_param*correct + (1|subj_id), data=full.sub)
@
%get table code
